\documentclass[11pt]{scrartcl}
\usepackage[sexy]{evan}
\usepackage{answers}

\begin{document}
\title{Nepal PreTST 2025 Solutions}
\author{Prakrit Gajurel}
\date{1 July 2026}
\maketitle

\section{Problems}

\begin{problem}
    Shining tells Prajit a positive integer $n \ge 2025$. Prajit then tries to place n points such that no four points are concyclic and no
    $3$ points are collinear in Euclidean plane, such that Shining cannot find a group of three points such that their circumcircle contains
    none of the other remaining points. Is he always able to do so?
\end{problem}

\begin{proof}

\end{proof}

\begin{problem}
    (a) Positive rational numbers $a, b,$ and $c$ have the property that $\frac{a}{b} + \frac{b}{c} + \frac{c}{a}$ is an integer. 
    Is it possible for $\frac{a}{c} + \frac{c}{b} + \frac{b}{a}$ to also be an integer except for the trivial solution?

    (b) Positive real numbers $a, b,$ and $c$ have the property that $\frac{a}{b} + \frac{b}{c} + \frac{c}{a}$ is an integer. 
    Is it possible for $\frac{a}{c} + \frac{c}{b} + \frac{b}{a}$ to also be an integer except for the trivial solution?
\end{problem}

\begin{proof}
    We solve part (b) first.
    \begin{remark}
        Note that the trivial solution is obviously $a=b=c$. However, it was mentioned in the contest that $a=b$ or any permutation of it is allowed,
        so we make full use of it below.
    \end{remark}
    \begin{claim}
        For positive real numbers $a$, $b$, $c$, it is possible.
    \end{claim}
    \begin{proof}
        Set $a=b$ and we get that the first expression and the second expression are equal. Therefore, we need to 
        find a value for $a$, $b$, and $c$ such that the expression is equal. This is obviously quite easy, we can just set $a=b=1$ and solve some 
        equation by setting
        \[
        1 + c + \frac 1c = k
        \]
        where $k$ is some integer. For our example let $k=4$, giving $c=\frac{3+\sqrt5}{2}$, which works upon checking and we're done.
    \end{proof}
\end{proof}

\begin{problem}
    Let the incircle of $\triangle ABC$ touch sides $BC$, $CA$, and $AB$ at points $D$, $E$, and $F$, respectively. Let $D'$ be the diametrically
    opposite point of $D$ with respect to the incircle. Let lines $AD'$ and $AD$ intersect the incircle again at $X$ and $Y$, respectively.
    Prove that the lines $DX$, $D'Y$, and $EF$ are concurrent, i.e., the lines intersect at the same point.
\end{problem}

\begin{proof}
    Define $T := D'Y \cup DX$, $Z := DD' \cup AT$, and denote by $I$ the incenter of $\triangle ABC$. Further let $\omega$ denote the
    incircle.
    Obviously $DD'$ is a diameter to the $\omega$, thus $D'Y \perp AD$ and $D'X \perp DT$, which also implies that $DZ \perp AT$. 
    This implies that all the points $A, F, I, E, Z$ lie on a circle with radius $AI$. Further, note $ADXZ$ is cyclic, 
    so by the radical axis theorem on the circles $(ADXZ)$, $(AFIE)$, and $\omega$ we get that $AZ$, $EF$, $DX$ concur at $T$.
    However as $T$ is also the intersection of lines $DX$ and $D'Y$, we get that $EF$, $DX$, and $D'Y$ concur at $T$,
    as desired.
    $(ADXZ)$ 
\end{proof}

\begin{problem}
    Find all pairs of positive integers \( n \) and \( x \) such that
    \[
    1^n + 2^n + 3^n + \cdots + n^n = x!
    \]
\end{problem}

\begin{proof}

\end{proof}

\end{document}